Quantitative Benchmarking for Automatically Generated Conjectures

### 2017-11-30 TEBenchmarkPaper/article.tex
Add Jianguo as co-author
Fix typo in code example

\author{Chris Warburton \and
        Alison Pease
        % TODO: Invite Katya? Even if she only offers some help, can acknowledge
}

@@

\institute{C. Warburton \at
           University of Dundee \\
           \email{c.m.warburton@dundee.ac.uk}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           A. Pease \at
           University of Dundee \\
           \email{a.pease@dundee.ac.uk}
}

@@

\begin{figure}
  \begin{equation*}
    \begin{split}
      \forall a. \Nil            &: \ListA                                  \\
      \forall a. \Cons           &: a \rightarrow \ListA \rightarrow \ListA \\
      \Head(\Cons(x, xs))        &= x                                       \\
      \Tail(\Cons(x, xs))        &= xs                                      \\
      \Append(\Nil,         ys)  &= ys                                      \\
      \Append(\Cons(x, xs), ys)  &= \Cons(x, \Append(xs, ys))               \\
      \Reverse(\Nil)             &= \Nil                                    \\
      \Reverse(\Cons(x, xs))     &= \Append(\Reverse(xs), \Cons(x, \Nil))   \\
      \Length(\Nil)              &= \Zero                                   \\
      \Length(\Cons(x, xs))      &= \Succ (\Length(xs))                     \\
      \Map(f, \Nil)              &= \Nil                                    \\
      \Map(f, \Cons(x, xs))      &= \Cons(f(x), \Map(f, xs))                \\
      \Foldl(f, x, \Nil)         &= x                                       \\
      \Foldl(f, x, \Cons(y, ys)) &= \Foldl(f, f(x, y), xs)                  \\
      \Foldr(f, \Nil,         y) &= y                                       \\
      \Foldr(f, \Cons(x, xs), y) &= f(x, \Foldr(f, xs, y))
    \end{split}
  \end{equation*}
  \caption{A simple theory defining a $\List$ type and some associated
    operations. $\Zero$ and $\Succ$ are from a Peano encoding of the
    natural numbers. Taken from
    \cite{Johansson.Dixon.Bundy:conjecture-generation}}
  \label{figure:list_theory}
\end{figure}

>>>>

\author{Chris Warburton \and
        Alison Pease    \and
        Jianguo Zhang
        % TODO: Invite Katya? Even if she only offers some help, can acknowledge
}

@@

\institute{C. Warburton \at
           University of Dundee \\
           \email{c.m.warburton@dundee.ac.uk}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           A. Pease \at
           University of Dundee \\
           \email{a.pease@dundee.ac.uk}
           \and
           J. Zhang \at
           University of Dundee \\
           \email{j.n.zhang@dundee.ac.uk}
}

@@

\begin{figure}
  \begin{equation*}
    \begin{split}
      \forall a. \Nil            &: \ListA                                  \\
      \forall a. \Cons           &: a \rightarrow \ListA \rightarrow \ListA \\
      \Head(\Cons(x, xs))        &= x                                       \\
      \Tail(\Cons(x, xs))        &= xs                                      \\
      \Append(\Nil,         ys)  &= ys                                      \\
      \Append(\Cons(x, xs), ys)  &= \Cons(x, \Append(xs, ys))               \\
      \Reverse(\Nil)             &= \Nil                                    \\
      \Reverse(\Cons(x, xs))     &= \Append(\Reverse(xs), \Cons(x, \Nil))   \\
      \Length(\Nil)              &= \Zero                                   \\
      \Length(\Cons(x, xs))      &= \Succ (\Length(xs))                     \\
      \Map(f, \Nil)              &= \Nil                                    \\
      \Map(f, \Cons(x, xs))      &= \Cons(f(x), \Map(f, xs))                \\
      \Foldl(f, x, \Nil)         &= x                                       \\
      \Foldl(f, x, \Cons(y, ys)) &= \Foldl(f, f(x, y), ys)                  \\
      \Foldr(f, \Nil,         y) &= y                                       \\
      \Foldr(f, \Cons(x, xs), y) &= f(x, \Foldr(f, xs, y))
    \end{split}
  \end{equation*}
  \caption{A simple theory defining a $\List$ type and some associated
    operations, taken from~\cite{Johansson.Dixon.Bundy:conjecture-generation}.
    $\Zero$ and $\Succ$ are from a Peano encoding of the natural numbers.}
  \label{figure:list_theory}
\end{figure}
